\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-23 paper/manuscript_paNote.tex
revised table
noted wget limitation in conclusion

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software dependency & \texttt{gov2text} inclusion \\
        \hline
        1. Assemble url list. & N/A & no \\
        2. Collect website files. & wget \& Selenium & no \\
        3. Remove names. & \texttt{spacyR} & yes \\
        4. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
        5. Lemmatize text. & \texttt{spacyR} & yes \\
        6. Retain tokens that are English words. & \texttt{Hunspell} & yes \\
        7. Convert corpus to document-term matrix. & [MARKUS?] & no \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
\end{table}

@@

>>>>

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software dependency & \texttt{gov2text} inclusion \\
        \hline
        1. Assemble url list. & Selenium & no \\
        2. Collect website files. & wget & no \\
        3. Lemmatize text. & \texttt{spacyR} & yes \\
        4. Remove names. & \texttt{spacyR} & yes \\
        5. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
        6. Retain tokens that are English words. & \texttt{Hunspell} & yes \\
        7. Removal of duplicate documents. & \texttt{gov2text} & \texttt{gov2text} \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
\end{table}

@@

The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files. By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript. For any one website, it would be possible to customize a routine with Selenium to access dynamic elements, but the process would need to be customized for each website. This would add a costly website-by-website step, whereas \texttt{wget} can be applied across websites without website-specific supervision.
